Market simulator

### 2020-10-21 analysis/05_market_simulator.Rmd
Org Inputs Finished

renderUI({

# Organization
selectInput(
  "org4_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(org_data[1:4,][which(org_data[1:4,5] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org4_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Refugee relief",
  selected = ifelse(
    sum(org_data[5:7,5]) == 0, "Emergency response",
    as.character(org_data[5:7,][which(org_data[5:7,5] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org4_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(org_data[8,5]) == 0, "Doesn’t engage in financial transparency",
    as.character(org_data[8,][which(org_data[8,5] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org4_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(org_data[9,5]) == 0, "Doesn’t engage in financial accountability",
    as.character(org_data[9,][which(org_data[9,5] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org4_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(org_data[10:11,5]) == 0, "Many small private donations",
    as.character(org_data[10:11,][which(org_data[10:11,5] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org4_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(org_data[12:13,5]) == 0, "Friendly relationship with government",
    as.character(org_data[12:13,][which(org_data[12:13,5] == 1), 1])
  ),
  width = "450px"
)
})
```

>>>>

  selectInput(
    "org4_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,5] == 1), 1]),
    width = "450px"
  )

  selectInput(
    "org4_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Refugee relief",
    selected = ifelse(
      sum(org_data[5:7,5]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,5] == 1), 1])
    ),
    width = "450px"
  )

  selectInput(
    "org4_fin_trans",
    label = "Financial Transparency:",
    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,5]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,5] == 1), 1])
    ),
    width = "450px"
  )

  selectInput(
    "org4_fin_account",
    label = "Financial Accountability:",
    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,5]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,5] == 1), 1])
    ),
    width = "450px"
  )

  selectInput(
    "org4_funding",
    label = "Funding Source:",
    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,5]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,5] == 1), 1])
    ),
    width = "450px"
  )

  selectInput(
    "org4_host_gov",
    label = "Relationship With Host Government",
    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,5]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,5] == 1), 1])
    ),
    width = "450px"
  )
